An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2011-11-26 Paper.tex
Rewrote code because of changes in other packages; debugged too

\bibliographystyle{abbrvnat}
\newcommand\citepos[2][]{\citeauthor{#2}'s \citeyearpar[#1]{#2}}
\newcommand\poscw{\citeauthor{ClW:06}'s \citeyearpar{ClW:06,ClW:07}}
\newcommand\citen[1]{\citeauthor{#1}, \citeyear{#1}}
\frenchspacing
\input{tex/simulationdefinitions}
\input{tex/empiricalresults}

@@

\begin{table}[tb]
  \centering
  \input{floats/simulation1}
\caption{Size and power of the \oos\ tests under \eqref{eq:dgp1} at
  10\% confidence.  These percentages are calculated from 5000
  samples.  Pr[\textsc{cw}] shows the fraction of simulations for which Clark
  and West's (2007) statistic rejects; Pr[new] shows the fraction of
  simulations for which this paper's test rejects; and Pr[disagree]
  gives the fraction of simulations in which this paper's test and
  Clark and West's (2007) give different conclusions.}
\label{tab:mc1}
\end{table}

@@

\begin{table}[tb]
  \centering
  \input{floats/simulation2}
\caption{Size and power of the \oos\ tests under \eqref{eq:dgp2} at
  10\% confidence.  These percentages are calculated from 5000
  samples.  Pr[\textsc{cw}] shows the fraction of simulations for which Clark
  and West's (2007) statistic rejects; Pr[new] shows the fraction of
  simulations for which this paper's test rejects; Pr[disagree] gives
  the fraction of simulations in which this paper's test and Clark and
  West's (2007) give different conclusions.}
\label{tab:mc2}
\end{table}

@@

Here, I conduct the same analysis, but using this paper's \mds\ test.
The benchmark model is the excess return's sample mean (as in the
original) and the alternative models are of the form
\[\text{excess return}_{t} = \alpha_{0} + \alpha_{1}\ 
\text{predictor}_{t-1} + \varepsilon_{t},\] where $\alpha_{0}$ and
$\alpha_{1}$ are estimated by \ols\ using a 10-year window.  The
predictors used are listed in the ``predictor'' column of
Table~\ref{tab:em1} \citep[see][for a detailed description of the
variables]{GoW:08}.  We also consider \citepos{CaT:08} proposed
correction to the models, that the forecasts be bounded below by zero
since negative forecasts are incredible, as well as two simple
combination forecasts, the mean and the median (over both the original
and the non-negative forecasts).  The data set is annual data
beginning in 1927 and ending in 2009, and the rolling window uses 10
observations.\footnote{This statistical analysis was conducted in R
  \citep{R} using the xtable \citep[version]{Dah:09}, Hmisc
  \citep[version]{Har:10}, and dbframe \citep[version 0.2.1]{Cal:10b}
  packages; please see the supplemental appendices for details on the
  programming \citep{Cal:11f,Cal:11g,Cal:11h}.}

Table~\ref{tab:em1} presents the results for each model.  The column
``value'' gives the value of the test statistic for each model, while
the ``naive'' and ``corrected'' columns indicate whether the statistic
is greater than the standard size-10\% critical value (1.28) and the
critical value estimated by the procedure of Theorem~\ref{res:2}
(\empiricalcriticalvalue).\footnote{The bootstrap uses 999
  replications with i.i.d. sampling, as proposed in Part~(\ref{it:1})
  of Theorem~\ref{res:2}.}  Three predictors are significant at the
naive critical values for both the original and bounded forecasts: the
dividend yield, long term interest rate, and book to market ratio.
But none are significant after accounting for data snooping, which
highlights the importance of these methods.  The median forecast is
significant using conventional critical values as well, but not the
corrected values.

>>>>

\bibliographystyle{abbrvnat}
\newcommand\citepos[2][]{\citeauthor{#2}'s \citeyearpar[#1]{#2}}
\newcommand\poscw{\citeauthor{ClW:06}'s \citeyearpar{ClW:06,ClW:07}}
\newcommand\citen[1]{\citeauthor{#1}, \citeyear{#1}}
\frenchspacing
\input{tex/simulationdefinitions}
\input{tex/empiricsdefinitions}
\input{tex/empiricalresults}

@@

\begin{table}[tb]
  \centering
  \input{floats/simulation1}
  \caption{Size and power of the \oos\ tests under \eqref{eq:dgp1} at
    \testsize\% confidence.  These percentages are calculated from \totalsims\
    samples.  Pr[\textsc{cw}] shows the fraction of simulations for which Clark
    and West's (2007) statistic rejects; Pr[new] shows the fraction of
    simulations for which this paper's test rejects; and Pr[disagree]
    gives the fraction of simulations in which this paper's test and
    Clark and West's (2007) give different conclusions.}
\label{tab:mc1}
\end{table}

@@

\begin{table}[tb]
  \centering
  \input{floats/simulation2}
  \caption{Size and power of the \oos\ tests under \eqref{eq:dgp2} at
    \testsize\% confidence.  These percentages are calculated from \totalsims\
    samples.  Pr[\textsc{cw}] shows the fraction of simulations for which Clark
    and West's (2007) statistic rejects; Pr[new] shows the fraction of
    simulations for which this paper's test rejects; Pr[disagree] gives
    the fraction of simulations in which this paper's test and Clark and
    West's (2007) give different conclusions.}
\label{tab:mc2}
\end{table}

@@

Here, I conduct the same analysis, but using this paper's \mds\ test.
The benchmark model is the excess return's sample mean (as in the
original) and the alternative models are of the form
\[\text{excess return}_{t} = \alpha_{0} + \alpha_{1}\ 
\text{predictor}_{t-1} + \varepsilon_{t},\] where $\alpha_{0}$ and
$\alpha_{1}$ are estimated by \ols\ using a \windowlength-year window.
The predictors used are listed in the ``predictor'' column of
Table~\ref{tab:em1} \citep[see][for a detailed description of the
variables]{GoW:08}.  We also consider \citepos{CaT:08} proposed
correction to the models, that the forecasts be bounded below by zero
since negative forecasts are incredible, as well as two simple
combination forecasts, the mean and the median (over both the original
and the non-negative forecasts).  The data set is annual data
beginning in 1927 and ending in 2009, and the rolling window uses
\windowlength\ observations.\footnote{This statistical analysis was
  conducted in R \citep{R} using the xtable \citep[version]{Dah:09},
  Hmisc \citep[version]{Har:10}, and dbframe \citep[version
  0.2.1]{Cal:10b} packages; please see the supplemental appendices for
  details on the programming \citep{Cal:11f,Cal:11g,Cal:11h}.}

Table~\ref{tab:em1} presents the results for each model.  The column
``value'' gives the value of the test statistic for each model, while
the ``naive'' and ``corrected'' columns indicate whether the statistic
is greater than the standard size-\bootsize\% critical value (1.28)
and the critical value estimated by the procedure of
Theorem~\ref{res:2} (\empiricalcriticalvalue).\footnote{The bootstrap
  uses \nboot\ replications with i.i.d. sampling, as proposed in
  Part~(\ref{it:1}) of Theorem~\ref{res:2}.}  Three predictors are
significant at the naive critical values for both the original and
bounded forecasts: the dividend yield, long term interest rate, and
book to market ratio.  But none are significant after accounting for
data snooping, which highlights the importance of these methods.  The
median forecast is significant using conventional critical values as
well, but not the corrected values.
